---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

oxforR is based on the Oxford COVID-19 Government Response Tracker (OxCGRT) and allows to retrieve their latest data in a R format. The tracker shows governmental responses to COVID-19 through 17 indicators for all countries. For further information, please visit their [website](https://www.bsg.ox.ac.uk/research/research-projects/coronavirus-government-response-tracker) and their [working paper](https://www.bsg.ox.ac.uk/research/publications/variation-government-responses-covid-19).

## Installation

You can install the released version of oxforR from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("warint/oxforR")
```


## Installation

You can install the current development version of 'oxforR' with:

```{r, eval = FALSE}
devtools::install_github("warint/oxforR")
```


## How-To

### Step 1: Getting the country's ISO code

A user needs to enter the ISO code of a country. To have access to this code, the following function provides this information.

```{r, eval = FALSE}
oxforr_country() # A list of all countries will be produced

oxforr_country(country = "Canada") # The ISO code for Canada will be produced

oxforr_country("Canada") # The ISO code for Canada will be produced
```

### Step 2: Getting the indicator's code

A user needs to enter the code of the desired indicator. To do so, the following function provides access to all the indicators of interest.

```{r, eval = FALSE}
oxforr_indicator() # A list of all indicators will be produced

oxforr_indicator(indicators = "public") # A list with all the variables including "public" will be produced

oxforr_indicator("public") # A list with all the variables including "public" will be produced
```


### Step 3: Getting the data

Once the user knows all the arguments, s.he can collect the data in a very easy way through this function:

```{r, eval=FALSE}

myData <-oxforr_data(country = "CAN",indicator = c("C1","C2")) 

myData <-oxforr_data(country = c("CAN","USA"),indicator = c("C1","C2"))

```
